---
title: "Fish Data"
---

## Description
The data-set contains the number of Fish a group of camper caught in a state park (taken from https://stats.idre.ucla.edu/r/dae/zip/). The task here is to predict the number of fish caught by a fishing party. We have a small data set, of 250 groups, which visited a state park and provided the following information:

- how many people are in the group
- the number children in the group
- the use of live bait
- whether the group came with a camper to the park.

```{r, echo=FALSE, eval=FALSE}
  # Importing of the data
  df <- read.csv("https://stats.idre.ucla.edu/stat/data/fish.csv")
  write.csv(df, "fish.csv", row.names = FALSE)
```



## Investiating the Zero Inflated Data

```{r plot_data, echo=TRUE, eval=TRUE}
data <- edudat::load_data("fish.csv")
plot(table(data$count), xlim=c(0, 10), col="lightblue", main="Histogram of Fish Caught", xlab="Number of Fish Caught")
```


## Investiating the Zero Inflated Data
```{r zib, echo=TRUE, eval=FALSE}
data <- edudat::load_data("fish.csv")
# Creating factor variables
data <- within(data, {
    nofish <- factor(nofish)
    livebait <- factor(livebait)
    camper <- factor(camper)
})
str(data)
library(pscl)
summary(m1 <- zeroinfl(count ~ child + camper | persons, data = data))
```

