---
title: "Wells Data"
---

## Description (from rstanarm)
A survey of 3200 residents in a small area of Bangladesh suffering from arsenic contamination of groundwater. 
Respondents with elevated arsenic levels in their wells had been encouraged to switch their water source to a safe public or private well in the nearby area (dist meters away) and the survey was conducted several years later to learn which of the affected residents had switched wells.

Souce: Gelman and Hill (2007)

3020 obs. of 5 variables

- switch Indicator for well-switching

- arsenic Arsenic level in respondent's well

- dist Distance (meters) from the respondent's house to the nearest well with safe drinking water.

- assoc Indicator for member(s) of household participate in community organizations

- educ Years of education (head of household)

Gelman, A. and Hill, J. (2007). Data Analysis Using Regression and Multilevel/Hierarchical Models. Cambridge University Press, Cambridge, UK. https://stat.columbia.edu/~gelman/arm/




```{r, echo=TRUE, eval=FALSE}
  # Importing of the data
  library(rstanarm)
  data(wells)
  ?wells
  write.csv(wells, "wells.csv", row.names = FALSE)
  
  if (FALSE){ 
    # More info
    install.packages("haven")
    library(haven)
    d = read_dta('/Users/oli/Downloads/ARM_Data/arsenic/all.dta')
  }
  
```



## Data

```{r plot_data, echo=TRUE, eval=TRUE}
data <- edudat::load_data("wells.csv")
summary(data)
```

```{r plot1, echo=FALSE, eval=FALSE}
library(ggplot2)

```

```{r plot, echo=FALSE, eval=FALSE}
library(ggplot2)
ggplot(wells, aes(x = dist, y = ..density.., fill = switch == 1)) +
  geom_density(alpha=0.5) +
  scale_fill_manual(values = c("gray30", "skyblue"))
```
So especially people which are living close to a contaminated well are more likely to switch to a safe well. 




